---
title: Comparison of TAF and icesTAF
output:
  pdf_document:
    toc: true
    number_sections: true
---

---

**Preamble**\

```{r}
library(diff)
tools.prod <- "~/git/ices/tools-prod"
```

\newpage

# R directory

```{r}
diff_dir(tools.prod)
```

Check out these files:

1. `draft.data.script.R`
2. `taf.roxygenise.R`

\newpage

# Namespace

```{r}
diff_namespace(tools.prod)
```

Check out these entries:

1. `export(draft.data.script)`
2. `export(taf.roxygenise)`
    * `S3method(roxy_tag_parse,roxy_tag_tafAccess)`
    * `S3method(roxy_tag_parse,roxy_tag_tafKey)`
    * `S3method(roxy_tag_parse,roxy_tag_tafOriginator)`
    * `S3method(roxy_tag_parse,roxy_tag_tafPeriod)`
    * `S3method(roxy_tag_parse,roxy_tag_tafSource)`
    * `S3method(roxy_tag_parse,roxy_tag_tafYear)`

\newpage

# Environment

```{r}
diff_environment()
```

Check out these objects:

1. `draft.data.script`
2. `taf.roxygenise`
   * `list2bibtex`
   * `loadpkg`
   * `roclet_output.roclet_taf`
   * `roclet_process.roclet_taf`
   * `roxy_tag_parse.roxy_tag_tafAccess`
   * `roxy_tag_parse.roxy_tag_tafKey`
   * `roxy_tag_parse.roxy_tag_tafOriginator`
   * `roxy_tag_parse.roxy_tag_tafPeriod`
   * `roxy_tag_parse.roxy_tag_tafSource`
   * `roxy_tag_parse.roxy_tag_tafYear`
   * `taf_roclet`

\newpage

# R files

```{r}
files <- intersect(dir(file.path(tools.prod, "TAF/R")),
                   dir(file.path(tools.prod, "icesTAF/R")))
diffs <- sapply(files, diff_file, tools.prod=tools.prod)
diffs <- diffs[!sapply(diffs, is.null)]
names(diffs)
```

Based on the `diff_file` output, 21 R files are different.

Let's look at each R file that is different. In many cases, the difference is
trivial, often from development responding to CRAN feedback when we submitted
the TAF package, so we can keep the TAF version. In other cases, where
discussion and/or action is needed, the $\Rightarrow$ sign is used and the
difference is highlighted and discussed in the next section.

\newpage

```{r}
diffs[1]
```
(Trivial)\newpage

```{r}
diffs[2]
```
(Trivial)\newpage

```{r}
diffs[3]
```
(Trivial)\newpage

```{r}
diffs[4]
```
(Trivial)\newpage

```{r}
diffs[5]
```
(Trivial)\newpage

```{r}
diffs[6]
```
(Trivial)\newpage

```{r}
diffs[7]
```
(Trivial)\newpage

```{r}
diffs[8]
```
(Trivial)\newpage

```{r}
diffs[9]
```
(Trivial)\newpage

```{r}
diffs[10]
```
(Trivial)\newpage

```{r}
diffs[11]
```
(Trivial)\newpage

```{r}
diffs[12]
```
(Trivial)\newpage

```{r}
diffs[13]
```
(Trivial)\newpage

```{r}
diffs[14]
```

$\Rightarrow$ This rewrite of `read.bib` (22 Mar 2021, Colin) removed the
dependency on the **jsonlite** package.

The **icesTAF** package has the old `read.bib` (28 Oct 2020, Colin) version that
depends on **jsonlite**. Implementing **icesTAF** as a layer on top of **TAF**,
this version will disappear.

\newpage

```{r}
diffs[15]
```
(Trivial)\newpage

```{r}
diffs[16]
```
(Trivial)\newpage

```{r}
diffs[17]
```
(Trivial)\newpage

```{r}
diffs[18]
```
(Trivial)\newpage

```{r}
diffs[19]
```
(Trivial)\newpage

```{r}
diffs[20]
```
(Trivial)\newpage

```{r}
diffs[21]
```
(Trivial)\newpage

# Discussion and actions

```{r}
diffs[14]
```

$\Rightarrow$ This rewrite of `read.bib` (22 Mar 2021, Colin) removed the
dependency on the **jsonlite** package.

The **icesTAF** package has the old `read.bib` (28 Oct 2020, Colin) version that
depends on **jsonlite**. Implementing **icesTAF** as a layer on top of **TAF**,
this version will disappear.

\newpage

# Conclusions

Implemented as a layer on top of **TAF**, the **icesTAF** package only includes
two user-level functions:

- `draft.data.script()`
- `taf.roxygenise()`

These are conveniently provided in two files: `draft.data.script.R` and
`taf.roxygenise.R`.
