---
title: Comparison of TAF and icesTAF
output:
  pdf_document:
    toc: true
    number_sections: true
---

---

**Preamble**\

```{r}
library(diff)
tools.prod <- "~/git/ices/tools-prod"
```

\newpage

# Files

```{r}
compare.files(tools.prod)
```

Check out these files:

1. `draft.data.script.R`
2. `get.stockassessment.results.R`
3. `get.stockassessments.R`
4. `taf.roxygenise.R`
5. `upload.fay.R`

\newpage

# Namespace

```{r}
compare.namespace(tools.prod)
```

Check out these entries:

1. `export(draft.data.script)`
2. `export(get.stockassessment.results)`
3. `export(get.stockassessments)`
4. `export(taf.roxygenise)`
    * `S3method(roxy_tag_parse,roxy_tag_tafAccess)`
    * `S3method(roxy_tag_parse,roxy_tag_tafKey)`
    * `S3method(roxy_tag_parse,roxy_tag_tafOriginator)`
    * `S3method(roxy_tag_parse,roxy_tag_tafPeriod)`
    * `S3method(roxy_tag_parse,roxy_tag_tafSource)`
    * `S3method(roxy_tag_parse,roxy_tag_tafYear)`
5. `export(upload.fay)`

\newpage

# Environment

```{r}
compare.environment()
```

Check out these objects:

1. `draft.data.script`

2. `taf.roxygenise`
   * `list2bibtex`
   * `loadpkg`
   * `roclet_output.roclet_taf`
   * `roclet_process.roclet_taf`
   * `roxy_tag_parse.roxy_tag_tafAccess`
   * `roxy_tag_parse.roxy_tag_tafKey`
   * `roxy_tag_parse.roxy_tag_tafOriginator`
   * `roxy_tag_parse.roxy_tag_tafPeriod`
   * `roxy_tag_parse.roxy_tag_tafSource`
   * `roxy_tag_parse.roxy_tag_tafYear`
   * `taf_roclet`
